Probability

### 2016-04-14 prob.tex
outline of example

\theoremstyle{remark}
\newtheorem{example}{Example}
\newcommand{\events}{\ensuremath{\mathcal{F}}}
\newcommand{\qevents}{\ensuremath{\mathcal{A}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}

@@

As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
space $\qevents$ to be the linear span of these operators:
\[
\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
\]
Each state $\psi$ of the Hilbert space induces a probability measure
$\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
\[
\phi_\psi(A) = \langle \psi ~|~ A\psi \rangle
\]

>>>>

\theoremstyle{remark}
\newtheorem{example}{Example}
\newcommand{\events}{\ensuremath{\mathcal{F}}}
\newcommand{\qevents}{\ensuremath{\mathcal{A}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}

@@

As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
space $\qevents$ to be the linear span of these operators:
\[
\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
\]
Each state $\ket{\psi}$ of the Hilbert space induces a probability
measure $\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
\[
\phi_\psi(A) = \ip{\psi}{A\ket{\psi}}
\]

Concrete example: consider the two qubit Hilbert space with
computational bases $\ket{0}$ and $\ket{1}$ and consider
the following families of projections:
\begin{itemize}
\item Family I: $\proj{0}$, $\proj{1}$
\item Family II: $\proj{+}$, $\proj{-}$
\end{itemize}
and consider the two states \ldots
